Faster generic IND-CCA2 secure KEM using ``encrypt-then-MAC''

### 2024-09-12 etm-transform/manuscript/main.tex
Need to extensively rewrite sectino 4

>>>>

\section{Implementation}\label{sec:implementation}
ML-KEM (based on \cite{bos2018crystals}\cite{avanzi2019crystals}) is an IND-CCA2 secure key encapsulation mechanism standardized by NIST in FIPS 203. ML-KEM achieves IND-CCA2 security first by constructing a public-key encryption scheme whose IND-CPA security is derived from the hardness of the module learning with error (MLWE) problems, then applying the Fujisaki-Okamoto transformation. We extended the reference C implementation of ML-KEM (https://github.com/pq-crystals/kyber) to implement our ``encrypt-then-MAC'' transformation and compared the performance characteristics of our instantiation with ML-KEM.

\subsection{Choosing a message authenticator}

\subsection{KEM performance}

\subsection{Key exchange performance}
